### 2016-08-30 version0.0/paper3.tex
Applying part of Sarah's comments on ch4

Some of the most tested methods of data mining in astronomy are artificial neural networks (ANNs)~\citep[e.g.][and references therein]{Hossein14,Hossein16}.
ANNs are spiered to work in the same way that the neurons work in a human brain.
These are networks of interconnected neurons (nodes), in which all of the connections are weighted.
These networks are used to study nonlinear and complex relations between input and output data.
One of the most well-known unsupervised neural networks in astronomy is a Kohonen self-organizing map (also called self-organizing map, or SOM).
SOMs visualize complex data~\citep{Kohonen82} and show simple geometrical relationships in non-linear high dimensional data~\citep{Kohonen98}.
The result of a SOM is a 1D or 2D network of neurons, which shows the positions of clusters and their relative distance.
Since the 1990s, many studies have utilized SOMs for object classification and clustering (e.g. classifying quasars' spectra, star/galaxy classifications, gamma-ray burst clustering and light curve classification) and photometric redshift estimation~\citep[e.g.][]{Odewahn92, Hernandez94, Murtagh95, Maehoenen95,Scaringi09,Geach12,Fustes13,Meusinger16}.

@@

    For the photometry part of the sample, we used the \GALEX \citep{Martin05} far-ultraviolet and near-ultraviolet (FUV and NUV) channel images; \halpha~(6574.7\AA), \sii~(6730.72\AA) and \oiii~(5024.9\AA) narrow band images~\citep{Massey07}, IRAC 3.6, 4.5, 5.8 and 8.0~$\mu$m images~\citep{Barmby06}; MIPS~24 and 70~$\mu$m~images~\citep{Gordon06}; and PACS 100 and 160~$\mu$m and SPIRE 250, 350, and 500~$\mu$m~\citep{Fritz12} images.
     The units of all fluxes were converted to W~m$^{-2}$ in order to be the same as the PAH fluxes.
     $^{12}$CO (J:$1\rightarrow0$) line emission images~\citep{Nieten06} and atomic gas (\hi) 21~cm emission images from~\cite{Chemin09} were added to the input data. 
     For derived values, we utilized SFR(FUV + 24$\mu$m) measured using combination of FUV and 24$\mu$m emission, stellar mass, molecular gas mass, atomic gas mass, total gas mass, and total infrared (TIR) luminosity (L$_\mathrm{TIR}$) from~\cite{Rahmani16}, and L$_\mathrm{dust}$ and dust mass from~\cite{Draine14}.

@@

     Correlations between some of single-wavelength emission and galaxy properties are well-known.
     Emission in the 3.6$\mu$m band traces the old stellar population very well~\citep[e.g.][]{Smith07a,Leitherer99} and it can be used to calculate the stellar mass~\citep{Eskew12}.
     FUV, \halpha, and TIR emission are indicators of star forming regions.
     In this project, we used the SFR traced by the FUV emission, corrected for foreground stars using NUV emission and for dust extinction using 24~$\mu$m emission.
     Total infrared emission is calculated from a modified version of~\cite{Draine07} calibrations using using 8, 24, 70, and 160~$\mu$m emission~\citep{Boquien10}.

@@

        Comparing the correlation coefficient plots for all 10 regions in M31 (Fig.~\ref{fig: cor_all}) and for the clustered data (Fig.~\ref{fig: cor_cluster1}) shows the differences between all 10 regions and clustered data and why regions 3 to 8 become separated from the other regions.
        The main features that differentiate these two plots are the anti-correlations between PAH features and RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.8~$\mu$m~emission.
        Additionally, for the PAH fluxes in Fig.~\ref{fig: cor_cluster1}, there are no significant correlations with PACS~100~$\mu$m, L$_\mathrm{dust}$, L$_\mathrm{TIR}$, SFR, or metallicity.
        The PAH fluxes correlate with the SPIRE emission, but to a lesser extent than for the data from all regions.

@@

        Correlations between PAH features and SFR, and L$_\mathrm{TIR}$ are well-studied~\citep[e.g.][]{Peeters04,Tielens08}. 
        Many groups have used PAH features as a tracer of SFR by finding correlations between 
        PAH emission and SFR derived from extinction-corrected \halpha~\citep[e.g.][]{Calzetti07,Khramtsova13,Shipley16}.
        These correlations are seen in Fig.~\ref{fig: cor_all}, when we considered the data from all regions, but not in Fig.~\ref{fig: cor_cluster1} when considering the clustered data.
        Note that, since there are only 6 regions in the clustered data, even one outlier in the data may cause the correlation coefficient to become insignificant.
        Further analyses show that the absence of correlations between PAH fluxes and SFR is because of one outlier: region 6. Region 6 is located in a FUV-bright region, which breaks the correlations. 
        When we disregard this region, high correlations between 6.2 to 17.0~$\mu$m~PAHs and SFR (and L$_\mathrm{TIR}$) reappear.

        Strong anti-correlations between 6.2 to 17.0~$\mu$m~main PAH features and RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.6~$\mu$m~emission in Fig.~\ref{fig: cor_cluster1} were not seen in Fig.~\ref{fig: cor_all} (even if we ignore the outlier values).
        Anti-correlations between PAH features and the \halpha, \sii, and \oiii~emission could be the result of one of the following. 
        First, the optical data are not corrected for dust extinction.
        The PAH features correlate with the amount of dust while \halpha~emission anti-correlates with the amount of dust due to extinction as suggested by \cite{Calzetti94}.
        Therefore, higher PAH fluxes imply higher dust abundance and less \halpha~emission, and the same holds for \sii~and \oiii~emission.
        Second is the possible effect of the structure of the observed regions.
        If the observed regions are located near the edge of \hii~regions we would expect to see more PAH and less \halpha~emission. 
        The anti-correlations between 6.2 to 17.0~$\mu$m~PAH features and RHI have been seen in other studies, as well~\citep[e.g.][]{Wu06, Gordon08,Calzetti10,Dim15}. 
        \cite{Wu06} suggested these anti-correlations could be the result of PAH destruction due to a high amount of harder radiation (thus higher RHI).
        On the other hand,~\cite{Gordon08} argued that the harder radiation could make the photodissociation regions (PDRs) smaller.
        The PAH features are mostly coming from the PDRs that are surrounded by \hii~regions, and the PAH features' underlying continuum emission is from the \hii~regions.
        Therefore, the lower flux of the PAH features could be the result of the smaller size of PDRs.%Els: If you have an harder radiation field, you destroy your smaller PAHs. Hence, simply a harder RHI does not argue for a smaller PDRs being more plausible. 
        The latter reason, which could also describe the anti-correlation between PAH features and \halpha~emission, seems to be the more probable one.

@@

    Regions 1 and 9 are close to each other and in the same side of the star forming ring. 
    However, region 1 is in an area of the galaxy with less diffuse \halpha~emission than region 9, which might be the reason for their distances in the SOM.
    Region 2 is more distant from other regions in the galaxy and located in the star forming ring.
    However, similar to regions 1 and 4, region 2 is located in an area of the galaxy with less diffuse \halpha~emission.
    Therefore, the place of region 2 in the SOM tends towards regions 1 and 4. 
    Region 10 is in the bulge of the galaxy, and its position on the SOM is isolated from all the other regions by a strip of a dark colours.

@@

            We increased the dimension of input data in Fig.~\ref{fig: only_pahs} (PAH-only data) gradually, by adding other quantities to the input data. 
            The order in which data were added is the same as the order in Fig.~\ref{fig: cor_all}, i.e. the SOM in Fig~\ref{fig: col3and11_dist} was created from PAH and \halpha\ emission as input data, the SOM in Fig~\ref{fig: col3and12_dist} created from PAHs, \halpha~emission and \sii~ continuum, and so on. 
            \import{../image_paper3/text_files/image_texts/}{col3byall.tex}

@@

            Comparing Figs.~\ref{fig: col3and11_dist} to~\ref{fig: col3and25_dist} shows that adding \halpha~emission data to PAH features causes regions 9 and 10 become isolated. 
            Increasing the dimension of the input data makes region 10 more isolated.
            The relative positions of regions 4 and 7 stay the same with increasing the dimensions of the input data. 
            Adding SPIRE 350, 500~$\mu$m emission and L$_{\rm dust}$ does not have any obvious effect on the networks.
            Stellar mass, total gas mass, dust mass and RHI data alternate the distances between neurons effectively, but it seems that adding SFR, L$_{\rm TIR}$ and metallicity data revokes those changes.

@@

Using smaller-sized self-organizing maps, we clustered M31 data into two major groups, which led us to correlations that could not have otherwise been seen without clustering.
Six of the regions in M31 create a subgroup with relatively lower mid- and far-infrared emission.
PAH fluxes in these regions are highly anti-correlated with \halpha, \sii, \oiii~and IRAC 5.8~$\mu$m emission, stellar mass and radiation hardness index.
These anti-correlations are insignificant when the full dataset is considered.
The most probable reason for PAHs to anti-correlate with optical emission lines and RHI is a harder radiation field.
This makes the size of \hii~regions bigger and the size of photo-dissociation regions smaller, causing more \halpha~emission and less PAH emission, respectively.

>>>>

Some of the most tested methods of data mining in astronomy are artificial neural networks (ANNs)~\citep[e.g.][and references therein]{Hossein14,Hossein16}.
ANNs are inspired to work in the same way that the neurons work in a human brain.
These are networks of interconnected neurons (nodes), in which all of the connections are weighted.
These networks are used to study nonlinear and complex relations between input and output data.
One of the most well-known unsupervised neural networks in astronomy is a Kohonen self-organizing map (also called self-organizing map, or SOM).
SOMs visualize complex data~\citep{Kohonen82} and show simple geometrical relationships in non-linear high dimensional data~\citep{Kohonen98}.
The result of a SOM is a 1D or 2D network of neurons, which shows the positions of clusters and their relative distance.
Since the 1990s, many studies have utilized SOMs for object classification and clustering (e.g. classifying quasars' spectra, star/galaxy classifications, gamma-ray burst clustering and light curve classification) and photometric redshift estimation~\citep[e.g.][]{Odewahn92, Hernandez94, Murtagh95, Maehoenen95,Scaringi09,Geach12,Fustes13,Meusinger16}.

@@

    For the photometry part of the sample, we used the \GALEX \citep{Martin05} far-ultraviolet and near-ultraviolet (FUV and NUV) channel images; \halpha (6574.7\AA), \sii~(6730.72\AA) and \oiii~(5024.9\AA) narrow band images~\citep{Massey07}, IRAC 3.6, 4.5, 5.8 and 8.0~$\mu$m images~\citep{Barmby06}; MIPS~24 and 70~$\mu$m~images~\citep{Gordon06}; and PACS 100 and 160~$\mu$m and SPIRE 250, 350, and 500~$\mu$m~\citep{Fritz12} images.
     The units of all fluxes were converted to W~m$^{-2}$ in order to be the same as the PAH fluxes.
     $^{12}$CO (J:$1\rightarrow0$) line emission images~\citep{Nieten06} and atomic gas (\hi) 21~cm emission images from~\cite{Chemin09} were added to the input data. 
     For derived values, we utilized SFR(FUV + 24$\mu$m) measured using combination of FUV and 24$\mu$m emission, stellar mass, molecular gas mass, atomic gas mass, total gas mass, and total infrared (TIR) luminosity (L$_\mathrm{TIR}$) from~\cite{Rahmani16}, and L$_\mathrm{dust}$ and dust mass from~\cite{Draine14}.

@@

     Correlations between some of single-wavelength emission and galaxy properties are well-known.
     Emission in the 3.6$\mu$m band traces the old stellar population very well~\citep[e.g.][]{Smith07a,Leitherer99} and it can be used to calculate the stellar mass~\citep{Eskew12}.
     FUV, \halphadot, and TIR emission are indicators of star forming regions.
     In this project, we used the SFR traced by the FUV emission, corrected for foreground stars using NUV emission and for dust extinction using 24~$\mu$m emission.
     Total infrared emission is calculated from a modified version of~\cite{Draine07} calibrations using using 8, 24, 70, and 160~$\mu$m emission~\citep{Boquien10}.

@@

        Comparing the correlation coefficient plots for all 10 regions in M31 (Fig.~\ref{fig: cor_all}) and for the clustered data (Fig.~\ref{fig: cor_cluster1}) shows the differences between all 10 regions and clustered data and why regions 3 to 8 become separated from the other regions.
        The main features that differentiate these two plots are the anti-correlations between PAH features and RHI, stellar mass, \halphadot, \sii, \oiii, and IRAC~5.8~$\mu$m~emission.
        Additionally, for the PAH fluxes in Fig.~\ref{fig: cor_cluster1}, there are no significant correlations with PACS~100~$\mu$m, L$_\mathrm{dust}$, L$_\mathrm{TIR}$, SFR, or metallicity.
        The PAH fluxes correlate with the SPIRE emission, but to a lesser extent than for the data from all regions.

@@

        Correlations between PAH features and SFR, and L$_\mathrm{TIR}$ are well-studied~\citep[e.g.][]{Peeters04,Tielens08}. 
        Many groups have used PAH features as a tracer of SFR by finding correlations between 
        PAH emission and SFR derived from extinction-corrected \halpha \citep[e.g.][]{Calzetti07,Khramtsova13,Shipley16}.
        These correlations are seen in Fig.~\ref{fig: cor_all}, when we considered the data from all regions, but not in Fig.~\ref{fig: cor_cluster1} when considering the clustered data.
        Note that, since there are only 6 regions in the clustered data, even one outlier in the data may cause the correlation coefficient to become insignificant.
        Further analyses show that the absence of correlations between PAH fluxes and SFR is because of one outlier: region 6. Region 6 is located in a FUV-bright region, which breaks the correlations. 
        When we disregard this region, high correlations between 6.2 to 17.0~$\mu$m~PAHs and SFR (and L$_\mathrm{TIR}$) reappear.

        Strong anti-correlations between 6.2 to 17.0~$\mu$m~main PAH features and RHI, stellar mass, \halphadot, \sii, \oiii, and IRAC~5.6~$\mu$m~emission in Fig.~\ref{fig: cor_cluster1} were not seen in Fig.~\ref{fig: cor_all} (even if we ignore the outlier values).
        Anti-correlations between PAH features and the \halphadot, \sii, and \oiii~emission could be the result of one of the following. 
        First, the optical data are not corrected for dust extinction.
        The PAH features correlate with the amount of dust while \halpha emission anti-correlates with the amount of dust due to extinction as suggested by \cite{Calzetti94}.
        Therefore, higher PAH fluxes imply higher dust abundance and less \halpha emission, and the same holds for \sii~and \oiii~emission.
        Second is the possible effect of the structure of the observed regions.
        If the observed regions are located near the edge of \hii~regions we would expect to see more PAH and less \halpha emission. 
        The anti-correlations between 6.2 to 17.0~$\mu$m~PAH features and RHI have been seen in other studies, as well~\citep[e.g.][]{Wu06, Gordon08,Calzetti10,Dim15}. 
        \cite{Wu06} suggested these anti-correlations could be the result of PAH destruction due to a high amount of harder radiation (thus higher RHI).
        On the other hand,~\cite{Gordon08} argued that the harder radiation could make the photodissociation regions (PDRs) smaller.
        The PAH features are mostly coming from the PDRs that are surrounded by \hii~regions, and the PAH features' underlying continuum emission is from the \hii~regions.
        Therefore, the lower flux of the PAH features could be the result of the smaller size of PDRs.%Els: If you have an harder radiation field, you destroy your smaller PAHs. Hence, simply a harder RHI does not argue for a smaller PDRs being more plausible. 
        The latter reason, which could also describe the anti-correlation between PAH features and \halpha emission, seems to be the more probable one.

@@

    Regions 1 and 9 are close to each other and in the same side of the star forming ring. 
    However, region 1 is in an area of the galaxy with less diffuse \halpha emission than region 9, which might be the reason for their distances in the SOM.
    Region 2 is more distant from other regions in the galaxy and located in the star forming ring.
    However, similar to regions 1 and 4, region 2 is located in an area of the galaxy with less diffuse \halpha emission.
    Therefore, the place of region 2 in the SOM tends towards regions 1 and 4. 
    Region 10 is in the bulge of the galaxy, and its position on the SOM is isolated from all the other regions by a strip of a dark colours.

@@

            We increased the dimension of input data in Fig.~\ref{fig: only_pahs} (PAH-only data) gradually, by adding other quantities to the input data. 
            The order in which data were added is the same as the order in Fig.~\ref{fig: cor_all}, i.e. the SOM in Fig~\ref{fig: col3and11_dist} was created from PAH and \halpha\ emission as input data, the SOM in Fig~\ref{fig: col3and12_dist} created from PAHs, \halpha emission and \sii~ continuum, and so on. 
            \import{../image_paper3/text_files/image_texts/}{col3byall.tex}

@@

            Comparing Figs.~\ref{fig: col3and11_dist} to~\ref{fig: col3and25_dist} shows that adding \halpha emission data to PAH features causes regions 9 and 10 become isolated. 
            Increasing the dimension of the input data makes region 10 more isolated.
            The relative positions of regions 4 and 7 stay the same with increasing the dimensions of the input data. 
            Adding SPIRE 350, 500~$\mu$m emission and L$_{\rm dust}$ does not have any obvious effect on the networks.
            Stellar mass, total gas mass, dust mass and RHI data alternate the distances between neurons effectively, but it seems that adding SFR, L$_{\rm TIR}$ and metallicity data revokes those changes.

@@

Using smaller-sized self-organizing maps, we clustered M31 data into two major groups, which led us to correlations that could not have otherwise been seen without clustering.
Six of the regions in M31 create a subgroup with relatively lower mid- and far-infrared emission.
PAH fluxes in these regions are highly anti-correlated with \halphadot, \sii, \oiii~and IRAC 5.8~$\mu$m emission, stellar mass and radiation hardness index.
These anti-correlations are insignificant when the full dataset is considered.
The most probable reason for PAHs to anti-correlate with optical emission lines and RHI is a harder radiation field.
This makes the size of \hii~regions bigger and the size of photo-dissociation regions smaller, causing more \halpha emission and less PAH emission, respectively.
